Summary of Difference

### 2020-04-02 scache/jpdc/tex/intro.tex
jpdc

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
% Several sophisticated frameworks are used in industrial big data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

@@

\begin{figure}
	\centering
	\includegraphics
		[width=.85\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
% As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk.  
% And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
And the \textit{shuffle read} fetches intermediate results from remote disks through the network. 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
Such task aggregation together with the coupled scheduling effectively simplifies task management.
% However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
However, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
% Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Moreover, since the shuffle read phase starts fetching data only after the corresponding reduce task starts, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
% Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
% Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
% As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
% To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as \textit{slow-start} from Hadoop MapReduce.
{\color{black}
% However, such early-start is by no means a panacea.
% This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% However, such early-start has several deficiencies.
% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
% Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

We evaluate SCache on a 50-node Amazon EC2 cluster on both Spark and Hadoop MapReduce.
In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS\footnote{http://www.tpc.org/tpcds/}, a standardized industry benchmark, on average on Apache Spark.

>>>>

\section{Introduction}\label{sec:introduction}
We are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
% Several sophisticated frameworks are used in industrial big data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
% Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

@@

\begin{figure}
	\centering
	\includegraphics
		[width=.95\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{chen2017parallel, sync, babu, tachyon, pacman, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
% In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
One of the major deficiency of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.
% In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
% As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk.  
% And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
And the \textit{shuffle read} fetches intermediate results from remote disks through the network. 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
Such task aggregation together with the coupled scheduling effectively simplifies task management.
% However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
However, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
% Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Moreover, since the shuffle read phase starts fetching data only after the corresponding reduce task starts, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
% Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
% Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
% As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
% To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as \textit{slow-start} from Hadoop MapReduce.
{\color{black}
% However, such early-start is by no means a panacea.
% This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% However, such early-start has several deficiencies.
% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
% Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

We evaluate SCache on a 50-node Amazon EC2 cluster on both Spark and Hadoop MapReduce.
In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS\footnote{http://www.tpc.org/tpcds/}, a standardized industry benchmark, on average on Apache Spark. On Apache Hadoop MapReduce, SCache also optimizes end-to-end Terasort completion time by $15\%$.

% This paper is the extension of our conference paper at PPoPP'18 \cite{fu2018efficient}.
% In this extended paper, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
% We use the model to evaluate the deficiencies of different resource scheduling strategies and optimize them.
% We also update the existing experiments with more comprehensive benchmarks and implement SCache on Hadoop MapReduce to demonstrates its compatibility and adaptability.

### 2020-04-02 scache/jpdc/tex/relatedwork.tex
jpdc

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and tries to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

@@

{\color{black}
\textbf{DAG Optimization.} 
% There are a number of studies on DAG optimization.
Slow-start from Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
% However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
In data skew mitigation, 
Skewtune \cite{skewtune} partitions the data dynamically. When a straggler task happens, it re-partitions the data and forces them to transfer to other nodes.
% But moving data may cause extra I/O overhead in computing.
LIBRA \cite{chen2014libra} proposes a new sampling method for DAG frameworks and uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.
Different from these works, SCache pre-schedules multiple shuffles and uses pre-fetching to gain optimization without breaking load balancing. 
%  by combining DAG information and heuristic algorithms.
% \textbf{Delay-scheduling} 
% Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
% ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
% At the same time, it achieves better data locality. 
% Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
% But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
% In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
}

@@

% \textbf{Network layer optimization.} 
% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
% BASS\cite{qin2017bandwidth} combines SDN (Software-defined networking) with Hadoop and provides a bandwidth-aware task scheduling to optimize shuffle phases.
% Hybrid SDN \cite{huang2018survey} can also be seen as a solution to improve the performance.
% We think that it can be applied on SCache to further improve the performace.
% To increase the scalability, hybrid SDN\cite{huang2018survey} can 
% Though the efforts above are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
% Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
% According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.

>>>>

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and tries to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

@@

{\color{black}
\textbf{DAG Optimization.} 
% There are a number of studies on DAG optimization.
Slow-start from Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
% However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
In data skew mitigation, 
Skewtune \cite{skewtune} partitions the data dynamically. When a straggler task happens, it re-partitions the data and forces them to transfer to other nodes.
% But moving data may cause extra I/O overhead in computing.
LIBRA \cite{chen2014libra} proposes a new sampling method for DAG frameworks and uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.
Different from these works, SCache pre-schedules multiple shuffles and uses pre-fetching to gain optimization without breaking load balancing. 
%  by combining DAG information and heuristic algorithms.
% \textbf{Delay-scheduling} 
% Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
% ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
% At the same time, it achieves better data locality. 
% Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
% But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
% In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
}

@@

\textbf{Network layer optimization.} 
% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
% BASS\cite{qin2017bandwidth} combines SDN (Software-defined networking) with Hadoop and provides a bandwidth-aware task scheduling to optimize shuffle phases.
% Hybrid SDN \cite{huang2018survey} can also be seen as a solution to improve the performance.
% We think that it can be applied on SCache to further improve the performace.
% To increase the scalability, hybrid SDN\cite{huang2018survey} can 
% Though the efforts above are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
Varys \cite{varys} and Aalo \cite{aalo} provide the network layer optimization for shuffle transfer. 
Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.

### 2020-04-02 scache/tii/coverletter/coverletter.tex
jpdc

% \author{Rui Ren}
% \author{Chunghsuan Wu}
% \author{Zhouwang Fu}
% \author{Tao Song}
% \author{Yanqiang Liu}
% \author{Zhengwei Qi}
% \author{Haibing Guan}

@@

% This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper is the extension of our conference paper at PPoPP. 
% In the manuscript we uploaded, we highlight the new content in blue.
% We believe that shuffle-heavy jobs are also existed widely in industrial big data analysis.
% SCache can also provide considerable optimization in industrial big data.
In this paper, we combine the characteristic of the industrial big data and DAG computing frameworks.
We provide a new data processing solution for the industrial big data based on our conference paper.
Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big data analysis.
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The FRQ model quantifies computing and I/O resources by five input parameters. 
Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
In this paper, we use the model to evaluate the deficiencies of different resources scheduling strategies and then optimize them.
\item 
In the conference paper, we only implement SCache on Spark. 
In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big data analysis.
% By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
% Meanwhile, our experiments are also consistent with the analysis of the model.
This result also demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
% To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
\item
We append two parts to the evaluation section. 
Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper (50-nodes m4.xlarge cluster).
According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
We believe that the added content makes a sufficient contribution to this special issue.
% We believe that the added content makes a sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
% \bibliography{coverletter}

>>>>

\author{Rui Ren}
\author{Chunghsuan Wu}
\author{Zhouwang Fu}
\author{Tao Song}
\author{Yanqiang Liu}
\author{Zhengwei Qi}
\author{Haibing Guan}

@@

This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
% This paper is the extension of our conference paper at PPoPP. 
% In the manuscript we uploaded, we highlight the new content in blue.
% We believe that shuffle-heavy jobs are also existed widely in industrial big data analysis.
% SCache can also provide considerable optimization in industrial big data.
% In this paper, we combine the characteristic of the industrial big data and DAG computing frameworks.
In this paper, we provide a new data processing solution for the industrial big data based on our conference paper.
Besides, we use the credible benchmark to demonstrate that our solution is effective in the big data analysis.
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The FRQ model quantifies computing and I/O resources by five input parameters. 
Furthermore, the FRQ model visualizes the resource scheduling strategies of the DAG frameworks in the time dimension. 
In this paper, we use the model to evaluate the deficiencies of different resources scheduling strategies and then optimize them.
\item 
In the conference paper, we only implement SCache on Spark. 
In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big data analysis.
% By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
% Meanwhile, our experiments are also consistent with the analysis of the model.
This result also demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
% To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
\item
We append two parts to the evaluation section. 
Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper (50-nodes m4.xlarge cluster).
According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
% We believe that the added content makes a sufficient contribution to this special issue.
We believe that the added content makes a sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
\bibliography{coverletter}
